### 2016-04-15 templates/report/research/tex/academic_works.tex
File created using the institution from the advisee.
NIRA-86 - Update the "Academic Work" class according to João's suggestions

{% block content %}
{% if postdoc_concluded or postdoc_in_progress or phd_concluded or phd_in_progress or msc_concluded or msc_in_progress %}
	{% if postdoc_concluded or postdoc_in_progress %}
\subsubsection{Post-doctoral fellows}
		{% if postdoc_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in postdoc_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if postdoc_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in postdoc_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}

{% if phd_concluded or phd_in_progress %}
\subsubsection{PhD thesis}
		{% if phd_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in phd_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if phd_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in phd_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}

{% if msc_concluded or msc_in_progress %}
\subsubsection{MSc dissertations}
		{% if msc_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in msc_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if msc_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in msc_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.institution }}
		{% if result.schollarship %}\item Schollarship: {{ result.schollarship }}{% endif %}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}

>>>>

{% block content %}
{% if postdoc_concluded or postdoc_in_progress or phd_concluded or phd_in_progress or msc_concluded or msc_in_progress %}
	{% if postdoc_concluded or postdoc_in_progress %}
\subsubsection{Post-doctoral fellows}
		{% if postdoc_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in postdoc_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if postdoc_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in postdoc_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing {% if result.end_date %}(as of {{ result.end_date }}){% endif %}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}

{% if phd_concluded or phd_in_progress %}
\subsubsection{PhD thesis}
		{% if phd_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in phd_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if phd_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in phd_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing {% if result.end_date %}(as of {{ result.end_date }}){% endif %}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}

{% if msc_concluded or msc_in_progress %}
\subsubsection{MSc dissertations}
		{% if msc_concluded %}
\paragraph{Concluded}
\begin{enumerate}
			{% for result in msc_concluded %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} to {{ result.end_date }}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
		{% if msc_in_progress %}
\paragraph{In progress}
\begin{enumerate}
			{% for result in msc_in_progress %}
	\item Title of the project: {{ result.title }}
	\begin{itemize}
		\item Period: {{ result.start_date }} - ongoing {% if result.end_date %}(as of {{ result.end_date }}){% endif %}
		\item Advisee: {{ result.advisee }}
		\item Advisor: {{ result.advisor }}
		{% if result.co_advisors %}\item Co-advisor: {{ result.co_advisors }}{% endif %}
		\item Institution: {{ result.advisee.institution }}
		{% if result.funding_agency %}\item Funding: {{ result.funding_agency }}{% endif %}
		{% if result.url %}\item Funding information: {{ result.url }}{% endif %}
		\item Abstract: {{ result.abstract }}
	\end{itemize}
             {% endfor %}
\end{enumerate}
		{% endif %}	
	{% endif %}
